Fig5

### 2020-05-08 analysis/figure-3.Rmd
working on new fig 4
now with temp fig 4

DEG_path <- "../results/DEseq2/hypothesis/"   # path to the data
DEG_files <- dir(DEG_path, pattern = "*DEGs") # get file names
DEG_pathfiles <- paste0(DEG_path, DEG_files)
#DEG_files

allDEG2 <- DEG_pathfiles %>%
  setNames(nm = .) %>% 
  map_df(~read_csv(.x), .id = "file_name") %>% 
  mutate(DEG = sapply(strsplit(as.character(file_name),'./results/DEseq2/hypothesis/'), "[", 2))  %>% 
  mutate(DEG = sapply(strsplit(as.character(DEG),'_diffexp.csv'), "[", 1))  %>% 
  mutate(tissue = sapply(strsplit(as.character(DEG),'\\.'), "[", 1)) %>%
  mutate(down = sapply(strsplit(as.character(DEG),'\\_'), "[", 3)) %>%
  mutate(up = sapply(strsplit(as.character(DEG),'\\_'), "[", 4)) %>%
  mutate(comparison = paste(down,up, sep = "_")) %>%
  mutate(sex = sapply(strsplit(as.character(sextissue),'\\_'), "[", 1)) %>%
  mutate(tissue = sapply(strsplit(as.character(sextissue),'\\_'), "[", 2)) %>%
dplyr::select(sex,tissue,comparison, direction, gene, lfc, padj, logpadj) 
head(allDEG2)

allDEG2$tissue <- factor(allDEG2$tissue, levels = tissuelevel)

allDEG2$comparison <- factor(allDEG2$comparison, levels = c("eggs_chicks", "lo_hi"))
allDEG2 <- allDEG2 %>% mutate(comparison = fct_recode(comparison, "lo vs. hi PRL   " = "lo_hi",
                                                      "eggs vs. chicks" = "eggs_chicks"))
allDEG2$direction <- factor(allDEG2$direction, levels = c("eggs", "chicks", "lo", "hi"))

PRLDEGs <- allDEG2 %>%
  filter(tissue == "pituitary", comparison == "lo vs. hi PRL   ",
         direction == "hi") %>%
  arrange(desc(logpadj))
PRLDEGs

envDEGs <- allDEG2 %>%
  filter(tissue == "pituitary", comparison == "eggs vs. chicks",
         direction == "chicks") %>%
  arrange(desc(logpadj))
envDEGs

hilogenes <- PRLDEGs %>% head(20) %>% distinct(gene) %>% pull(gene)
eggchickgenes <- envDEGs %>% head(20) %>% distinct(gene) %>% pull(gene)

hypothesisDEGs <- c(hilogenes, eggchickgenes, WGCNAgenes) %>% unique()

>>>>

#deg wrangling moved to datawrangling.R

hypothesisDEGs <- c(hypothesisDEGs, WGCNAgenes) %>% unique()

### 2020-05-08 analysis/figure-4.Rmd
now with temp fig 4

```{r fig5, fig.width=7, fig.height=7}

@@

b <- plottsneelipsev2(pittsne, pittsne$treatment, allcolors ) + labs(subtitle = "pituitary ~ parental stage", x = NULL) + facet_wrap(~sex, scales = "free")

c <- plottsneelipsev2(pittsne, pittsne$extint, allcolors ) + labs(subtitle = "pituitary ~ external enviornment", x = NULL) + facet_wrap(~sex, scales = "free")

d <- plottsneelipsev2(pittsne, pittsne$hiloPRL, allcolors ) + labs(subtitle = "pituitary ~ internal physiology", x = NULL) + facet_wrap(~sex, scales = "free")

bcd <- plot_grid(b,c,d, nrow = 1)

b <- plotcandidatemanipquad(candidatevsd, "hypothalamus", c("DRD1")) 
c <- plotcandidatemanipquad(candidatevsd2,"pituitary", c("PRL")) 
d <- plotcandidatemanipquad(candidatevsd,"gonad", c("PGR"))

plot_grid(a, b,c,d , ncol = 1, rel_heights = c(1,1,1,1))

@@

## supplementary figs

```{r}

b <- plottsneelipsev2(hyptsne, hyptsne$treatment, allcolors) + labs(subtitle = "hypothalamus ~ parental stage", x = NULL)  + facet_wrap(~sex, scales = "free")

d <- plottsneelipsev2(gontsne, gontsne$treatment, allcolors ) + labs(subtitle = "gonads ~ parental stage")  + facet_wrap(~sex, scales = "free")

e <- plottsneelipsev2(hyptsne, hyptsne$hiloPRL, allcolors ) + labs(subtitle = "hypothalamus ~ internal physiology", x = NULL) + facet_wrap(~sex, scales = "free")

g <- plottsneelipsev2(gontsne, gontsne$hiloPRL, allcolors ) + labs(subtitle = "gonads ~ internal physiology" ) + facet_wrap(~sex, scales = "free")

efg <- plot_grid(e,f,g, nrow = 3, labels = c("d"), label_size = 8, rel_heights = c(1,1,1))

h <- plottsneelipsev2(hyptsne, hyptsne$extint, allcolors ) + labs(subtitle = "hypothalamus ~ external enviornment", x = NULL) + facet_wrap(~sex, scales = "free")

j <- plottsneelipsev2(gontsne, gontsne$extint, allcolors ) + labs(subtitle = "gonads ~ external enviornment" ) + facet_wrap(~sex, scales = "free")

>>>>

```{r fig4, fig.width=7.25, fig.height=7.25}

@@

b1 <- plotcandidatemanipquad(candidatevsd, "hypothalamus", c("DRD1")) 
b2 <- plotcandidatemanipquad(candidatevsd2,"pituitary", c("PRL")) 
b3 <- plotcandidatemanipquad(candidatevsd,"gonad", c("PGR"))

b <- plot_grid(b1,b2,b3, ncol = 1)

c1 <- plottsneelipsev2(hyptsne, hyptsne$treatment, allcolors) + 
  labs(subtitle = "Hypothalamus ", x = NULL)  
c2 <- plottsneelipsev2(hyptsne, hyptsne$extint, allcolors ) + 
  labs(subtitle = " ", x = NULL) + 
  theme(axis.text.y = element_blank(), axis.title.y = element_blank())
c3 <- plottsneelipsev2(hyptsne, hyptsne$hiloPRL, allcolors ) + 
  labs(subtitle = " ", x = NULL) + 
  theme(axis.text.y = element_blank(), axis.title.y = element_blank()) 
c4 <- plottsneelipsev2(pittsne, pittsne$treatment, allcolors ) + 
  labs(subtitle = "Pituitary ", x = NULL) 
c5 <- plottsneelipsev2(pittsne, pittsne$extint, allcolors ) + 
  labs(subtitle = " ", x = NULL) + 
  theme(axis.text.y = element_blank(), axis.title.y = element_blank()) 
c6 <- plottsneelipsev2(pittsne, pittsne$hiloPRL, allcolors ) + 
  labs(subtitle = " ", x = NULL) + 
  theme(axis.text.y = element_blank(), axis.title.y = element_blank())
c7 <- plottsneelipsev2(gontsne, gontsne$treatment, allcolors ) + 
  labs(subtitle = "Ggonads ")  
c8 <- plottsneelipsev2(gontsne, gontsne$extint, allcolors ) + 
  labs(subtitle = " " )    +
  theme(axis.text.y = element_blank(), axis.title.y = element_blank())
c9 <- plottsneelipsev2(gontsne, gontsne$hiloPRL, allcolors ) + 
  labs(subtitle = " " ) + 
  theme(axis.text.y = element_blank(), axis.title.y = element_blank())

c <- plot_grid(c1,c2,c3,c4,c5,c6,c7,c8,c9, nrow = 3)

bc <- plot_grid(b, c, nrow = 1, labels = c("", "C"), label_size = 8)

plot_grid(a, bc, ncol = 1, rel_heights  = c(0.25,1),
          labels = "AUTO", label_size = 8)

@@
